Informative Autonomous Sampling of Oceanographic Variables Using Joint Excursion Sets

### 2019-10-07 main_new.tex
Updates from Overleaf
updated abstract

% "Title of the paper"
\title{Informative Oceanographic Sampling using Excursion Probabilities for Multivariate Random Fields}
\runtitle{Excursion Probabilities for Informative Sampling}

@@

\begin{abstract}
  Improving and optimizing oceanographic sampling is a crucial task
  for marine science and maritime management. Faced with limited
  resources to understand dynamic processes in the water-column, the
  combination of statistics and autonomous robotics can provide
  opportunities for studying experimental design for effective
  characterization of oceanographic phenomena. In this work we develop
  methods for efficient spatial sampling applied to the mapping of
  coastal processes by providing informative descriptions of spatial
  characteristics of ocean phenomena. Specifically, we define a design
  criterion based on reducing uncertainty in the joint excursions of
  random fields, and derive analytical expressions for the expected
  Bernoulli variance reduction in the excursion set of spatial
  temperature and salinity variables. We show how these can be
  applicable in static and sequential designs, building on myopic and
  look-ahead sampling strategies. We use simulations to study the
  properties and differences between state-of-the-art approaches
  followed by results from field deployments with an autonomous
  underwater vehicle as part of a case study mapping the boundary of a
  river plume. The results demonstrate the ability of the methods to
  effectively inform and execute data-driven environmental sampling.

>>>>

% "Title of the paper"
\title{Informative Autonomous Sampling of Oceanographic Variables Using Joint Excursion Sets}
\runtitle{Excursion Probabilities for Informative Sampling}

@@

\begin{abstract}
  Improving and optimizing oceanographic sampling is a crucial task
  for marine science and maritime management. Faced with limited
  resources to understand dynamic processes in the water-column, the
  combination of statistics and autonomous robotics provide
  opportunities for studying experimental design. In this work we develop
  methods for efficient spatial sampling applied to the mapping of
  coastal processes by providing informative descriptions of spatial
  characteristics of ocean phenomena. Specifically, we define a design
  criterion based on reducing uncertainty in the joint excursions of
  random fields, and derive analytical expressions for the expected
  Bernoulli variance reduction in the excursion set of spatial
  temperature and salinity variables. We show how these can be
  applicable in static and sequential designs, building on myopic and
  non-myopic sampling strategies. We use simulations to study the
  properties and differences between state-of-the-art approaches
  followed by results from field deployments with an autonomous
  underwater vehicle as part of a case study mapping the boundary of a
  river plume. The results demonstrate the potential of combining statistical methods and robotic platforms, and the abilities of the derived methods to effectively inform and execute data-driven environmental sampling.
